Finite-state morphological transducers for three Kypchak languages

### 2013-10-11 kipchak-lrec-2013/kipchak-paper.tex
add bibitem
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@47983 72bbbca6-d526-0410-a7d9-f06f51895060
some fixes and additions
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48028 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}
\usepackage{multirow}

@@

\title{Finite-state morphological transducers for three Kipchak languages}

@@

\cite{washington2012}
\cite{salimzyanov2013}

@@

>>>>

\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{multirow}

\usepackage{booktabs}

\setromanfont{DejaVu Serif}

@@

\title{Finite-state morphological transducers for three Kypchak languages}

@@

The Northwestern branch of Turkic is often referred to as the Kypchak branch, and can be divided into three subbranches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the south Kypchak group \citep[82-83]{histofturkic}.  The geographic distribution of the languages is shown in map \ref{}.

\cite{washington2012}
\cite{salimzyanov2013}
\cite{bekmanova2013}

@@

\begin{table}
\begin{center}
\begin{tabular}{lrr}
\textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\hline
wikipedia & 850K &  - \\
Äwezov & 155K & - \\
RFERL 2010 & 3.2M & - \\
bible & 577K & - \\
quran & 107K & - \\
\hline
\end{tabular}
 \caption{Corpora used for coverage of Kazakh}
 \label{table:corpora-kaz}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{llrr}
\toprule
\textbf{Language} & \textbf{Corpus} & \textbf{Words} & \textbf{Coverage} \\
\midrule
\multirow{6}{*}{Kazakh} & wikipedia 2011& 850K &  - \\
	& Äwezov & 155K & - \\
	& RFERL 2010 & 3.2M & - \\
	& bible & 577K & - \\
	& quran & 107K & - \\\cline{2-4}
	& average & - & 90.5\% \\
\midrule
\multirow{5}{*}{Tatar} & wikipedia 2013 & 128K &  - \\
	& news 2005-2011 & 4.6M & - \\
	& new testament & 137K & - \\
	& quran & 165K & - \\
	& Aytmatov & 5K & - \\\cline{2-4}
	& average & - & 89.0\% \\
\midrule
\multirow{4}{*}{Kumyk} & yoldash & 287K &  - \\
	& new testament & 154K & - \\
	& book of Genesis & 28K & - \\\cline{2-4}
	& average & - & 88.0\% \\
\bottomrule
\end{tabular}
 \caption{Corpora used for coverage tests}
 \label{table:corpora}
\end{center}
\end{table}
